An asymptotically normal out-of-sample test based on mixed estimation windows

### 2015-01-09 appendix.tex
Last minute changes before ECMA sub

\begin{rthm}{\ref{res:1}}\input{mixedwindow_thm1}\end{rthm}
\begin{proof}
  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
  \begin{equation}\label{eq:6}
    \sqrt{P} (\fb - \E \fb^*)
    = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
  \end{equation}
  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
  we can use a Taylor expansion to rewrite~\eqref{eq:6} as
  \begin{align*}
    \sqrt{P} (\fb - \E \fb^*)
    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
  \end{align*}
  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
  Lemma~\ref{res:a4} shows that
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:11} \\
    \WesB \to^{p} 0 \label{eq:12} \\
    \intertext{and}
    \WesC \to^{p} 0 \label{eq:13}
  \end{gather}
  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
  w_t = o_{p}(1)$. The proof that
  \begin{equation*}
    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
  \end{equation*}
  follows the same argument as in \citet{Wes:96}.
\end{proof}

\begin{rlem}{\ref{lem:2}}\input{mixedwindow_lem2}\end{rlem}
We will only prove $\sigmah_2 \to^p \sigma$. The result for
$\sigmah_1$ is essentially the same, but uses \citepos{JoD:00} Theorem
2.1 instead of an application of the \lln.
\begin{proof}
  First, we can rewrite the components of the variance estimator as
  \begin{align*}
    \sh_{21} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]^2 \\
    \sh_{22} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]
                        \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb - \E g_t)\Big]
    \intertext{and}
    \sh_{23} &= \oavg{t} \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb + \E g_t)\Big]^2
  \end{align*}
  so $\sigmah_2 \to^p \sigma$ as long as the following hold:
  $\fb - \E \fb^* \to^p 0$,
  $\gb - \E \gb^* \to^p 0$,
  \begin{gather}
    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:1} \\
    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:3} \\
    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:7} \\
    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
    \intertext{and}
    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
  \end{gather}
  The first two results are implied by the proof of Theorem~\ref{res:1}
  and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7} follow from the \lln, so it
  suffices to prove~\eqref{eq:4} and~\eqref{eq:5}.

@@

\noindent%
This Lemma establishes that \citepos{Wes:96} basic results hold under
our weaker moment and dependence conditions and provides several
extensions for the first few observations. To streamline the
presentation, we'll assume in these proofs that $x_t$ is a scalar.
\begin{proof}
  We will prove each part in order.
  \begin{enumerate}
  \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
    of size $-1/2$; let $c_t$ and $\zeta_k$ denote its mixingale
    constants and coefficients. Note that, for any $b$, $t^{b} x_t \ep_{t+1}$ is
    also an $L_2$-mixingale array with constants $t^{b} c_s$ and
    coefficients $\zeta_k$, since
    \begin{align*}
      \| \E_{t-k} t^{b} x_t \ep_{t+1} \| &= t^{b} \| \E_{t-k} x_t \ep_{t+1} \| \\
      &\leq (t^{b} c_t) \zeta_k
    \end{align*}
    and
    \begin{align*}
      \| t^{b} x_t \ep_{t+1} - t^{b} \E_{t+k} x_t \ep_{t+1} \| &= t^{b} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
      &\leq (t^{b} c_t) \zeta_{k+1}.
    \end{align*}

@@

\begin{proof}
We can write
\begin{equation*}
  \Big\lvert \WesA \Big\rvert \leq
  \Big\lVert \ocltb{t} (F_t - F) B \Big\rVert \;
  \omaxb{t} \lVert H_t \rVert.
\end{equation*}
From Lemma~\ref{res:a2}, $\omaxb{t} \lVert H_t \rVert \to^p 0$. The \clt\ implies
that $\ocltb{t} (F_t - F) = O_p(1)$,
establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
and~\eqref{eq:13} are similar.
\end{proof}

>>>>

Note that Assumptions~\ref{a1} and~\ref{a3} imply that $f_t$, $g_t$,
and $F_t$ are all strong mixing of size $-r/(r-2)$ or uniform mixing
of size $-r/(2r-2)$ and are stationary with bounded $r$th moments.

\begin{rthm}{\ref{res:1}}\input{mixedwindow_thm1}\end{rthm}
\begin{proof}
  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
  \begin{equation}\label{eq:6}
    \sqrt{P} (\fb - \E \fb^*)
    = \ocltb{t} ((f_t - \E f_t) + (\fh_t - f_t))
      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
  \end{equation}
  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
  we can use a Taylor expansion to rewrite~\eqref{eq:6} as
  \begin{align*}
    \sqrt{P} (\fb - \E \fb^*)
    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
  \end{align*}
  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
  Lemma~\ref{res:a4} shows that
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:11} \\
    \WesB \to^{p} 0 \label{eq:12} \\
    \intertext{and}
    \WesC \to^{p} 0 \label{eq:13}
  \end{gather}
  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
  w_t = o_{p}(1)$. The proof that
  \begin{equation*}
    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
  \end{equation*}
  follows the same argument as in \citet{Wes:96} and \citet{Mcc:00}.
\end{proof}

\begin{rlem}{\ref{lem:2}}\input{mixedwindow_lem2}\end{rlem}
\noindent%
We will only prove $\sigmah_2 \to^p \sigma$. The result for
$\sigmah_1$ is essentially the same and uses \citepos{JoD:00} Theorem
2.1 for the \hac\ equivalent of Equations~\eqref{eq:1}--\eqref{eq:7}.
\begin{proof}
  First, we can rewrite the components of the variance estimator as
  \begin{align*}
    \sh_{21} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]^2 \\
    \sh_{22} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]
                        \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb - \E g_t)\Big]
    \intertext{and}
    \sh_{23} &= \oavg{t} \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb + \E g_t)\Big]^2
  \end{align*}
  so $\sigmah_2 \to^p \sigma$ as long as the following hold:
  $\fb - \E \fb^* \to^p 0$,
  $\gb - \E \gb^* \to^p 0$,
  \begin{gather}
    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:1} \\
    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:3} \\
    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:7} \\
    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
    \intertext{and}
    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
  \end{gather}
  The first two results are implied by the proof of
  Theorem~\ref{res:1} and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7}
  follow from the \lln, since each summand is an $L_1$-mixingale of
  size $-1$ \citep[see, for example][Theorem 17.5]{Dav:94}, so it suffices to
  prove~\eqref{eq:4} and~\eqref{eq:5}.

@@

\noindent%
To streamline the
presentation, we'll assume in these proofs that $x_t$ is a scalar.
\begin{proof}
  We will prove each part in order.
  \begin{enumerate}
  \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
    of size $-1/2$ \citep[see Theorem 17.5 of][]{Dav:94}; let $c_t$
    and $\zeta_k$ denote its mixingale
    constants and coefficients. Note that, for any $b$, $t^{b} x_t \ep_{t+1}$ is
    also an $L_2$-mixingale array with constants $t^{b} c_s$ and
    coefficients $\zeta_k$, since
    \begin{align*}
      \| \E_{t-k} t^{b} x_t \ep_{t+1} \| &= t^{b} \| \E_{t-k} x_t \ep_{t+1} \| \\
      &\leq (t^{b} c_t) \zeta_k
    \end{align*}
    and
    \begin{align*}
      \| t^{b} x_t \ep_{t+1} - t^{b} \E_{t+k} x_t \ep_{t+1} \| &= t^{b} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
      &\leq (t^{b} c_t) \zeta_{k+1}.
    \end{align*}

@@

\begin{proof}
We can write
\begin{equation*}
  \Big\lvert \WesA \Big\rvert \leq
  \Big\lVert \ocltb{t} (F_t - F) B \Big\rVert \;
  \omaxb{t} \lVert H_t \rVert.
\end{equation*}
From Lemma~\ref{res:a2}, $\omaxb{t} \lVert H_t \rVert \to^p
0$. \citepos{Jon:97} \clt\ implies that $\ocltb{t} (F_t - F) =
O_p(1)$, establishing~\eqref{eq:11}. The proofs of \eqref{eq:12}
and~\eqref{eq:13} are similar.
\end{proof}

### 2015-01-09 mixedwindow.tex
Last minute changes before ECMA sub

\section{Theoretical results supporting the asympotically normal \oos\ statistic}
\label{sec:1}

@@

This paper proposes using the same basic \oos\ statistic,
but using a recursive window to estimate $\btrue$ and produce
$\eph_{t+1}$:
\begin{align}
  \label{eq:8}
  \bh_t &= \Big(\sum_{s=1}^{t-1} x_{s} x_{s}'\Big)^{-1}
  \sum_{s=1}^{t-1} x_{s} y_{s+1}
  && \text{and}
  &
  \eph_{t+1} &= y_{t+1} - x_t'\bh_t
\end{align}
for each $t$.
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \oclt{t} \Big[(y_{t+1} -
  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under Clark and West's
\mds\ null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
another forecast of $y_{t+1}$ based on a fixed-length rolling window.

@@

The main conditions on the \dgp\ are summarized in the first
assumption.  The weak dependence and moment conditions are
standard. These assumptions are slightly weaker than similar
assumptions in \citet{Wes:96} and \citet{Mcc:00}, but only because we
make use of more recent developments in limit theory, in particular
the \clt\ for Near-Epoch Dependent (\ned) processes proven by
\cite{Jon:97} and the \fclt\ of \cite{JoD:00b}.

\begin{asmp}\label{a1}%
  The data are generated by the relationship
  \begin{equation}
    y_{t+1} = x_t'\btrue + \ep_{t+1}
  \end{equation}
  for $t=1,2,\dots$, for some value $\btrue$, with $\E x_t \ep_{t+1} =
  0$, $\E \ep_{t+1}^2 > 0$, and $\E x_t x_t'$ positive definite for
  all $t$. Also assume that there is an additional sequence of random
  vectors $z_t$ and the processes $\ep_{t+1}$, $x_t$, and $z_t$ are
  $L_2$-\ned\ of size $-(r-1)/(r-2)$ for $r > 2$ on either a strong
  mixing process of size $-r/(r-2)$ or a uniform mixing process of
  size $-r/(2r-2)$.
\end{asmp}

@@

\begin{asmp}\label{a3}%
  The benchmark forecast is $x_t'\bh_t$, where $\bh_t$ is constructed
  with a recursive window according to~\eqref{eq:8}; the partial sums
  $\sum_{s=1}^{t-1} x_s x_s' / (t-1)$ are almost surely invertible for
  all $t \geq R$ (uniformly in $T$).  The alternative forecast
  satisfies
  \begin{equation}
    \yh_{1,t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
  \end{equation}
  where $\psi$ is a known measurable function and the window length,
  $R$, remains finite as $T \to \infty$. Moreover, the vector
  $(\ep_{t+1}, x_t, \yh_{t+1})$ has uniformly bounded $2 r$ moments and is
  4th order stationary.
\end{asmp}

The requirement that the alternative forecast satisfies moment
conditions, rather than the underlying predictors $z_t$, is somewhat
unappealing but necessary. The function $\psi$ that generates these
forecasts is otherwise nearly unrestricted, so even well-behaved predictors
could produce arbitrarily badly-behaved forecasts. For example, if
\begin{equation*}
  z_t \sim \iid~\bernoulli(1/2),
\end{equation*}
setting $\psi(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
since the forecast equals positive infinity with probability $1/2$. It
is easy to construct less obvious examples of problematic functions as
well. Assumption~\ref{a3} implicitly rules out these functional forms
by imposing moment conditions on the alternative models' forecasts.
The stationarity condition holds whenever the vector
$(\ep_{t+1}, x_t, z_t)$ is strictly stationary.

@@

The test statistic proposed in Theorem~\ref{thm:3} can be easily
extended in several ways. For longer-horizon forecasts (two or more
periods ahead), $\sigmah_1$ will remain consistent but $\sigmah_2$
will not --- the forecast errors for a correctly specified
$h$-step-ahead forecast have an MA($h-1$) dependence structure --- but
using a generalized $\sigmah_2$ that reflects this covariance
structure restores consistency. To test optimality under loss
functions other than squared-error, one can replace the forecast error
with the generalized forecast error \citep[see, for
example][]{PaT:07,PaT:07b} and replace the \ols\ estimator of $\beta$ with the
corresponding $M$-estimator. And the benchmark model can be replaced
in general with a nonlinear model that satisfies the assumptions of
\citet{Wes:96} or \citet{Mcc:00} by making the appropriate changes to
$f_t$ and $g_t$. (See \citealp{Wes:96} and \citealp{Mcc:00}
for details.) The general approach of using a recursive window to
estimate the benchmark and a fixed-length rolling window to estimate
the alternative applies quite broadly.

>>>>

\section{Theoretical results supporting the asymptotically normal \oos\ statistic}
\label{sec:1}

@@

This paper proposes using the same basic \oos\ statistic,
but using a recursive window to estimate $\btrue$ and produce
$\eph_{t+1}$:
\begin{align}
  \label{eq:8}
  \bh_t &= \Big(\sum_{s=1}^{t-1} x_{s} x_{s}'\Big)^{-1}
  \sum_{s=1}^{t-1} x_{s} y_{s+1}
  && \text{and}
  &
  \eph_{t+1} &= y_{t+1} - x_t'\bh_t
\end{align}
for each $t$.%
\footnote{The matrix inversion in $\bh_t$ can be replaced with a
  pseudo-inverse if necessary for some values of $t$ without changing
  the forecast.} %
\citepos{Wes:96} Theorem 4.1 implies that
\begin{equation*}
  \oclt{t} \Big[(y_{t+1} -
  x_t\bh_t)^2 - (y_{t+1} - v_t)^2 + (x_t'\bh_t - v_t)^2 \Big]
\end{equation*}
is asymptotically normal with mean zero under Clark and West's
\mds\ null for fairly
arbitrary processes $v_t$, as long as $v_t$ is weakly dependent and
the \oos\ statistic has uniformly positive variance.  Just as in
\citet{ClW:06,ClW:07}, these conditions are ensured if $v_t$ is
another forecast of $y_{t+1}$ based on a fixed-length rolling window.

@@

The main conditions on the \dgp\ are summarized in the first
assumption.  The weak dependence and moment conditions are
standard. The assumption of strict stationarity is stronger than
necessary in practice --- once the alternative forecasting method is
known, it is only necessary that the \oos\ adjusted loss difference be
weak stationary, and even that can be relaxed further --- but this
stronger assumption ensures that the results hold generally.

\begin{asmp}\label{a1}%
  The data are generated by the relationship
  \begin{equation}
    y_{t+1} = x_t'\btrue + \ep_{t+1}
  \end{equation}
  for $t=1,2,\dots$, for some value $\btrue$, with $\E x_t \ep_{t+1} =
  0$, $\E \ep_{t+1}^2 > 0$, and $\E x_t x_t'$ positive definite for
  all $t$. Also assume that there is an additional sequence of random
  vectors $z_t$ and the process $(\ep_{t+1}, x_t, z_t)$ is stationary
  and strong mixing of size $-r/(r-2)$ or uniform mixing of size
  $-r/(2r-2)$, for $r > 2$.
\end{asmp}

@@

\begin{asmp}\label{a3}%
  The benchmark forecast is $x_t'\bh_t$, where $\bh_t$ is constructed
  with a recursive window according to~\eqref{eq:8}. The alternative
  forecast satisfies
  \begin{equation}
    \yh_{t+1} = \psi(y_t,z_t,\dots,y_{t-R+1}, z_{t-R+1})
  \end{equation}
  where $\psi$ is a known measurable function and the window length,
  $R$, remains finite as $T \to \infty$. Moreover, the vector
  $(\ep_{t+1}, x_t, \yh_{t+1})$ has uniformly bounded $2 r$ moments
  where $r$ is first defined in Assumption~\ref{a1}.
\end{asmp}

The requirement that the alternative forecast satisfies moment
conditions, rather than the underlying predictors $z_t$, is somewhat
unappealing but necessary. The function $\psi$ that generates these
forecasts is otherwise nearly unrestricted, so even well-behaved predictors
could produce arbitrarily badly-behaved forecasts. For example, if
\begin{equation*}
  z_t \sim \iid~\bernoulli(1/2),
\end{equation*}
setting $\psi(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
since the forecast equals positive infinity with probability $1/2$. It
is easy to construct less obvious examples of problematic functions as
well. Assumption~\ref{a3} implicitly rules out these functional forms
by imposing moment conditions on the alternative models' forecasts.

@@

The test statistic proposed in Theorem~\ref{thm:3} can be easily
extended in several ways. For longer-horizon forecasts (two or more
periods ahead), $\sigmah_1$ will remain consistent but $\sigmah_2$
will not --- the forecast errors for a correctly specified
$h$-step-ahead forecast have an MA($h-1$) dependence structure --- but
using a generalized $\sigmah_2$ that reflects this covariance
structure restores consistency. To test optimality under loss
functions other than squared-error, one can replace the forecast error
with the generalized forecast error \citep[see, for
example][]{PaT:07,PaT:07b} and replace the \ols\ estimator of $\beta$ with the
corresponding $M$-estimator. And the benchmark model can be replaced
in general with a nonlinear model that satisfies the assumptions of
\citet{Wes:96} or \citet{Mcc:00} by making the appropriate changes to
$f_t$ and $g_t$. (See \citealp{Wes:96}, and \citealp{Mcc:00},
for details.) The general approach of using a recursive window to
estimate the benchmark and a fixed-length rolling window to estimate
the alternative applies quite broadly.
